Many Analystis Project

### 2022-03-03 analysis-religious-only.Rmd
updated analysis

d1 <- df %>%
  dplyr::filter(
   #  !is.na(wb_psychANXIETY),
   #  !is.na(age),
   #  !is.na(rel_CHURCHFREQ),
   # # !is.na(wb_psychMEANING),
   #  !is.na(male),
   #  !is.na(rel_EXTENTBELIEVEGOD),
  ) %>%
  dplyr::mutate(
    anx = as.integer(6- wb_psychANXIETY), # reverse coded! rescale 1-5
    religious = as.integer(IS_RELIIGOUS), #(1= religious, 2= not religious, 3=atheist) [R]
    #put outcome in ST units (see McElreath 2021)  # not necessary
    #age_s = scale(age),
    ch = rel_CHURCHFREQ,
  #  mn  = wb_psychMEANING,
    edu = education,
    bg =  rel_EXTENTBELIEVEGOD#,
  #  ch_s = scale(rel_CHURCHFREQ),
  #  mn_s = scale(wb_psychMEANING),
   # bg_s = scale(rel_EXTENTBELIEVEGOD)
  ) %>%
  dplyr::select(anx,
                ch,
                age,
                ses,
                #    mn,
                edu,
                bg,
                # anx_s,
                # age_s,
                #  ch_s,
                #  mn_s,
                edu,
                country,
                male,
                religious,
                #   bg_s,
                wb_psychANXIETY)

@@

@@

# fine, well below 10
max(dr$ipwCH)

dr$ch_ord <- factor(dr$ch, ordered=TRUE)
table(dr$ch_ord)

@@

plot_grand_mean_ameR + plot_grand_mean_ordR + plot_annotation(tag_levels = "a",  title = "Religious only model")
yola

ggsave(
  plot_grand_mean_ameR,
  path = here::here("figs"),
  width = 12,
  height = 6,
  units = "in",
  filename = "plot_grand_mean_ameR.jpg",
  device = 'jpeg',
  limitsize = FALSE,
  dpi = 1200
)

@@

@@

church_plot <-plot(ggeffects::ggemmeans(b_or, terms = "ch_ord")) +   xlab("Service attendance (standardised)") + ylab ("Anxiety (standardised)") + labs(title = "Baysian Multi-level Model",
subtitle = "Inverse Probability Weighting") + scale_y_continuous(limits = c(-.5,.5))+ 
  theme_classic()
church_plot

# pord<-brms::conditional_effects(b_or, "ch_ord", 
#                               spaghetti = T,
#                               ndraws = 1000,
#                               categorical = F,
#                               prob = .9,
#                               method = 'fitted')
# 
# 
# church_plot <- plot(pord, plot = FALSE)[[1]]   +  xlab("Service attendance (standardised)") + ylab ("Anxiety (standardised)") + labs(title = "Baysian Multi-level Model",
# subtitle = "Inverse Probability Weighting") + scale_y_continuous(limits = c(-.5,.5))+ 
#   theme_classic()
# church_plot
library(tidybayes)

@@

plot_grand_mean_ord <- ggplot(grand_mean_autonomy_dist, 
                                   aes(x = .epred, 
                                       fill = ch_ord)) +
  scale_fill_okabe_ito() +
    stat_halfeye(slab_alpha = 0.7) +
    scale_x_continuous(limits=c(-.6,.4)) +
  labs(x = "Predicted anxiety (standardised)", y = "Density",
       fill = "Church frequency",
       subtitle = "Posterior predictions: monotonic model") +
  theme_classic() +
     theme(legend.position = "bottom",
         legend.title = element_text(size = 12),
          legend.text = element_text(size = 8))

@@

plot_result_ord <- plot_grand_mean_ame + plot_grand_mean_ord+  plot_annotation(tag_levels = "a")
plot_result_ord

@@

@@

ggsave(
  plot_result_full,
  path = here::here("figs"),
  width = 12,
  height = 6,
  units = "in",
  filename = "plot_result_full.jpg",
  device = 'jpeg',
  limitsize = FALSE,
  dpi = 1200
)

@@

˝#\# Simulation tables

>>>>

d1 <- df %>%
  dplyr::filter(
   #  !is.na(wb_psychANXIETY),
   #  !is.na(age),
   #  !is.na(rel_CHURCHFREQ),
   # # !is.na(wb_psychMEANING),
   #  !is.na(male),
   #  !is.na(rel_EXTENTBELIEVEGOD),
  ) %>%
  dplyr::mutate(
    anx = as.integer(6- wb_psychANXIETY), # reverse coded! rescale 1-5
    religious = as.integer(IS_RELIIGOUS), #(1= religious, 2= not religious, 3=atheist) [R]
    #put outcome in ST units (see McElreath 2021)  # not necessary
    #age_s = scale(age),
    ch = rel_CHURCHFREQ,
  #  mn  = wb_psychMEANING,
    edu = education,
    bg =  rel_EXTENTBELIEVEGOD#,
  #  ch_s = scale(rel_CHURCHFREQ),
  #  mn_s = scale(wb_psychMEANING),
   # bg_s = scale(rel_EXTENTBELIEVEGOD)
  ) %>%
  dplyr::select(anx,
                ch,
                age,
                ses,
                #    mn,
                edu,
                bg,
                # anx_s,
                # age_s,
                #  ch_s,
                #  mn_s,
                edu,
                country,
                male,
                religious,
                #   bg_s,
                denomination,
                wb_psychANXIETY)

@@

table

```{r}
lt <-table1::table1(~  denomination, data = d1, transpose=F)
lt
lt <-table1::table1(~ ch + religious + age + male + edu + ses + denomination |country, data = d1, transpose=F)
lt
kable(as.data.frame(lt), booktabs=TRUE, "latex")

nrow(dr)
```

@@

# fine, well below 10
max(dr$ipwCH)
```

## Tables

```{r}
lt <-table1::table1(~ religious|ch_ord, data = dp)

kable(as.data.frame(lt), booktabs=TRUE, "latex")

nrow(dr)
```

### Simulation

```{r}
#\begin{lstlisting}[language=R]

set.seed(123)
sim_fun_A = function() {
  n <- 1000
  U <- rnorm(n, 1) # Unmeasured distress 
  A <- rnorm(n, 1) # religious service attendance,
  M <- rnorm(n , A + U)# rel id
  Y <- rnorm(n , - A*.2 + U + M*.1) #  distress reduced by attendance.

# Religious id, caused by attendance + distress

# simulate data
simdat_A <- data.frame(
  M = L, # rel id
  A = A, # rel service
  U = U, # distressing events (unmeasured)
  Y = Y ) # outcome

sim_A <- lm(Y ~ A + M, data = simdat_A)
sim_A
}

# Replicate including the mediator
r_lm_A <- NA
r_lm_A = replicate(100, sim_fun_A(), simplify = FALSE )

# average over outcomes: effect of religion is attenuated
parameters::pool_parameters(r_lm_A)

## Repeat but with no mediator in model
set.seed(123)
sim_fun_B = function() {
  n <- 1000
  U <- rnorm(n, 1) # Unmeasured distress 
  A <- rnorm(n, 1) # religious service attendance,
  M <- rnorm(n , A + U)# rel id + distress
  Y <- rnorm(n , - A *.2 + U + M*.1) #  distress reduced by attendance.

# simulate data
simdat_B <- data.frame(
  M = L, # rel id
  A = A, # rel service
  U = U, # distressing events (unmeasured)
  Y = Y ) # outcome

# Only exposure
sim_B <- lm(Y ~ A, data = simdat_A)
sim_B
}

# Replication 1000xs
r_lm_B <- NA
r_lm_B = replicate(100, sim_fun_B(), simplify = FALSE )

# average over outcomes: effect of religion is attenuated
parameters::pool_parameters(r_lm_B)

#\end{lstlisting}
```

```{r}
dr$ch_ord <- factor(dr$ch, ordered=TRUE)
table(dr$ch_ord)

@@

graph_r<- plot_grand_mean_ameR + plot_grand_mean_ordR + plot_annotation(tag_levels = "a",  title = "Religious only model")
yola

ggsave(
  graph_r,
  path = here::here("figs"),
  width = 12,
  height = 6,
  units = "in",
  filename = "graph_r.jpg",
  device = 'jpeg',
  limitsize = FALSE,
  dpi = 1200
)

@@

## Table
parameters::parameters(
  modmc_wt_priorStrong,
  test = "pd",
  component = "all",
  priors = FALSE, 
  ci_method = "hdi",
#  effects = "fixed",
  group_level = FALSE,
  diagnostic = "Rhat") %>%
    mutate_if(is.numeric, ~ round(., 3)) %>%
    mutate_all(funs(str_replace(., "b_", ""))) %>%
    mutate_all(funs(str_replace(., "bs", ""))) %>%
    kable(booktabs = T, "latex", caption =  "Parameter estimates for continuous (spline) model of religious service on anxiety") %>%
    print()

@@

church_plot <-plot(ggeffects::ggemmeans(b_or, terms = "ch_ord")) +   xlab("Service attendance (standardised)") + ylab ("Anxiety (standardised)") + labs(title = "Baysian Multi-level Model",
subtitle = "Inverse Probability Weighting") + scale_y_continuous(limits = c(-.5,.5))+ 
  theme_classic()
church_plot
```

## Tables

```{r}
# tab_or <- model_parameters(b_or,   verbose = F, ci_method = "hdi",test = c("pd"))
# kbl(tab_or, "latex",booktabs=T)

# sjstats::tidy_stan(tab_or)

# library(broom.mixed)
# tidy(
#   b_or,
#  # parameters = NA,
#   effects = c("fixed", "ran_pars"),
#   robust = FALSE,
#   conf.int = TRUE,
#   conf.level = 0.95,
#   conf.method = c("HPDinterval"),
#   fix.intercept = TRUE
# )

parameters::parameters(
  b_or,
  test = "pd",
  component = "all",
  priors = FALSE, 
  ci_method = "hdi",
#  effects = "fixed",
  group_level = FALSE,
  diagnostic = "Rhat") %>%
    mutate_if(is.numeric, ~ round(., 3)) %>%
    mutate_all(funs(str_replace(., "b_", ""))) %>%
    mutate_all(funs(str_replace(., "_moch", ""))) %>%
    kable(booktabs = T, "latex", caption =  "Parameter estimates for model of religious service on anxiety") %>%
    print()
```

```{r}
# pord<-brms::conditional_effects(b_or, "ch_ord", 
#                               spaghetti = T,
#                               ndraws = 1000,
#                               categorical = F,
#                               prob = .9,
#                               method = 'fitted')
# 
# 
# church_plot <- plot(pord, plot = FALSE)[[1]]   +  xlab("Service attendance (standardised)") + ylab ("Anxiety (standardised)") + labs(title = "Baysian Multi-level Model",
# subtitle = "Inverse Probability Weighting") + scale_y_continuous(limits = c(-.5,.5))+ 
#   theme_classic()
# church_plot
library(tidybayes)

@@

grand_mean_autonomy_dist2 <- b_or %>% 
  epred_draws(newdata = expand_grid(ch_ord = c("never",">1xpw")), 
              re_formula = NA)

plot_grand_mean_ord <- ggplot(grand_mean_autonomy_dist, 
                                   aes(x = .epred, 
                                       fill = ch_ord)) +
  scale_fill_okabe_ito() +
    stat_halfeye(slab_alpha = 0.7) +
    scale_x_continuous(limits=c(-.6,.4)) +
  labs(x = "Predicted anxiety (standardised)", y = "Density",
       fill = "Church frequency",
       subtitle = "Posterior predictions: monotonic model") +
  theme_classic() +
     theme(legend.position = "bottom",
         legend.title = element_text(size = 10),
          legend.text = element_text(size = 8))

@@

plot_grand_mean_ord2 <- ggplot(grand_mean_autonomy_dist2, 
                                   aes(x = .epred, 
                                       fill = ch_ord)) +
  scale_fill_okabe_ito() +
    stat_halfeye(slab_alpha = 0.7) +
    scale_x_continuous(limits=c(-.6,.4)) +
  labs(x = "Predicted anxiety (standardised)", y = "Density",
       fill = "Church frequency",
       subtitle = "Posterior predictions: monotonic model") +
  theme_classic() +
     theme(legend.position = "bottom",
         legend.title = element_text(size = 12),
          legend.text = element_text(size = 8))

plot_grand_mean_ord2

@@

plot_result_ord2 <- plot_grand_mean_ame + plot_grand_mean_ord2+  plot_annotation(tag_levels = "a")
plot_result_ord2

ggsave(
  plot_result_ord2,
  path = here::here("figs"),
  width = 12,
  height = 6,
  units = "in",
  filename = "plot_result_ord2.jpg",
  device = 'jpeg',
  limitsize = FALSE,
  dpi = 1200
)

@@

ggsave(
  plot_result_full,
  path = here::here("figs"),
  width = 10,
  height =10,
  units = "in",
  filename = "plot_result_full.jpg",
  device = 'jpeg',
  limitsize = FALSE,
  dpi = 1000
)

@@

˝## Simulation tables

### 2022-03-03 analysis-v-2.Rmd
updated analysis

```{r runanalysis, echo=FALSE, include = FALSE}
# source("libs.R") # libraries 
# source("funs.R") # custom functions
library("tidyverse")
library("easystats")
library("ggplot2") #plots
#library("sjstats") #test statistics
#library("sjPlot")
#library("sjmisc")
##library("insight")
#library("see")
#library("performance")
library("ggraph")
#library("parameters")
library("lme4")
#library("psych") ## correlation matrix
library("table1")
library("ggeffects")
#library("gghighlight")
#library("texreg")
library("kableExtra")
#library("naniar") # missingness
library("Amelia")
#library("magrittr")
library("patchwork")
library("texreg")
library("viridisLite")
library("patchwork")
library("here")
#library("rethinking")
#library("statsExpressions")
#library("ggstatsplot")
library("ggthemes")
=library("rstan")
library("brms")
library("tidybayes")
library("bayesplot")
library("dagitty")
library("ggdag")
library("geepack")  # marginal structural models
library("ipw") # inverse probability weighting. 
library("WeightIt")# inverse probability weighting. 
rstan_options(auto_write=TRUE)
options(mc.cores=parallel::detectCores ())
theme_set(theme_few())
```

@@

df <- d %>%
  dplyr::mutate(male2 = ifelse(gender != "man", 1 , 2)) %>% # for index categorical variable, not change of meaning for gender. male and people who do not identify as male.
  dplyr::mutate(male = factor(ifelse(gender != "man", "male" , "notmale"))) %>%
  rename(
    rel_CHURCHFREQ   = rel_1,
    # factor need to recode (eg 7 as 0)// yikes factor transformed into a number
    rel_PRAYERFREQ = rel_2,
    # factor need to recode (eg. 7 as 0)// yikes factor transformed into a number
    IS_RELIIGOUS = rel_3,
    # factor 1 = yes, 2 = no, 3 = atheist// yikes factor transformed into a number
    BELONGS_DENOMINATION = rel_4,
    # relig
    rel_EXTENTBELIEVEGOD = rel_5,
    # do you belong to a religion or religious denomination? 1 = yes, 2 = no (!)
    rel_EXTENTBELIEVEAFTERLIFE = rel_6,
    rel_EXTENTSPIRITUAL  = rel_7,
    rel_IMPORTANCERELIGIOUSLIFE = rel_8,
    # 1 to five
    rel_IMPORTANCEBELIEVEGOD = rel_9,
    # 1 to five
    wb_genLIFEQUALITY = wb_gen_1,
    # not defined # also remove second underscore, which BRMS doesn't like
    wb_genSATHEALTH = wb_gen_2,
    # not defined
    wb_phyPAIN = wb_phys_1,
    wb_physNEEDSMEDICALTREAT =  wb_phys_2,
    wb_physHASENERGY =  wb_phys_3,
    wb_physMOBILITY = wb_phys_4,
    wb_physSLEEP = wb_phys_5,
    wb_physCANDODAILYACTIVITIES  = wb_phys_6,
    wb_physSATCAPACITYWORK  = wb_phys_7,
    wb_psychENJOYLIFE = wb_psych_1,
    wb_psychMEANING  = wb_psych_2,
    wb_psychCONCENTRATE  = wb_psych_3,
    wb_psychLIKESAPPEARANCE  = wb_psych_4,
    wb_psychSATSELF  = wb_psych_5,
    wb_psychANXIETY  = wb_psych_6,
    wb_socSATPERSONALRELATIONSHIPS  = wb_soc_1,
    wb_socSATSUPPORTFRIENDS  = wb_soc_2
    #   wb_socSATSEX   = wb_soc_3,
  ) %>%
  dplyr::mutate(
    IS_RELIIGOUS = as.factor(IS_RELIIGOUS),
    denomination = as.factor(denomination),
    ethnicity = as.factor(ethnicity),
    country = as.factor(country)
  ) %>%
  dplyr::mutate(
    IS_RELIIGOUS = recode_factor(
      IS_RELIIGOUS,
      "0" = "atheist",
      "0.5" = "not_religious",
      "1" = "religious"
    )
  )

@@

```{r cache = TRUE}
library("naniar")
vis_miss(df) # substantial pattern of missingness in a few variables, 
df
df$wb_soc_3
dff<-df%>%
  select(-wb_soc_3)
sum(is.na(df$education))

miss_graph<- gg_miss_upset(dff)
miss_graph
# save graph
ggsave(
  dg1,
  path = here::here("Figs"),
  width = 10,
  height = 5,
  units = "in",
  filename = "dag_church.jpg",
  device = 'jpeg',
  limitsize = FALSE,
  dpi = 1200
)

@@

```{r}
library(mice)
d2<-mice(d1)
d3<-complete(d2)
saveRDS(d3,here::here("mods","d3"))
d3 <-readRDS(here::here("mods","d3"))
d4<-d3%>%
  select(anx, ch, bg, age, edu,male,ses,country)%>%
  drop_na()%>%
  mutate(anx_s = scale(anx),
         bg_s = scale(bg),
         ch_s = scale(ch),
         age_s = scale(age),
         edu_s = scale(edu),
         ses_s = scale(ses),
         male_2 =scale(as.numeric(male))/2,
         ses_s = scale(ses),
         country=as.factor(country))

@@

dbl <- ipw::ipwpoint(
  exposure = bg_g,
  family = "gaussian",
  numerator = ~ 1,
  denominator = ~ age_s +ch_s + edu_s + male_2 + ses_s + country,
  trunc = 0.01,
  data = as.data.frame(d4)
)

@@

ipb_bg<- geeglm(
  anx_s ~ bg_s,
  data = d1p,  
  id = country,
  corstr = "exchangeable",
  weights = ipwBG
)

ipb_ch<- geeglm(
  anx_s ~  ch_s,
  data = d1p,  
  id = country,
  corstr = "exchangeable",
  weights = ipwCH
)

@@

ipb_bg_noweights <- geeglm(
  anx_s ~ bg_s + ch_s + age_s + edu_s + male_2 + ses_s,
  data = d1p,  
  id = country,
  corstr = "exchangeable"
)

ipb_ch_noweights <- geeglm(
  anx_s ~ ch_s + age_s + edu_s + male_2 + ses_s,
  data = d1p,  
  id = country,
  corstr = "exchangeable"
)

model_parameters(ipb_bg_noweights)
model_parameters(ipb_bg)

model_parameters(ipb_ch_noweights)
model_parameters(ipb_ch)
```

@@

listout <- readRDS(here::here("mods","listout"))
modmc <- brm_multiple(
  anx_s ~ ch_s + age_s + edu_s + male_2 +ses_s + (1 + ch_s | country),
  data = listout,
  seed = 1234,
  warmup = 1000,
  iter = 2000,
  chains = 4,
  backend = "cmdstanr",
  threads = threading(4)
)

#saveRDS(modmc, here::here("mods", "modmc.rds"))
summary(modmc)
```

@@

>>>>

```{r runanalysis, echo=FALSE, include = FALSE}
# source("libs.R") # libraries 
# source("funs.R") # custom functions

library("tidyverse")
library("easystats")
library("ggplot2") #plots
#library("sjstats") #test statistics
#library("sjPlot")
#library("sjmisc")
##library("insight")
#library("see")
#library("performance")
library("ggraph")
#library("parameters")
library("lme4")
#library("psych") ## correlation matrix
library("table1")
library("ggeffects")
#library("gghighlight")
#library("texreg")
library("kableExtra")
#library("naniar") # missingness
library("Amelia")
#library("magrittr")
library("patchwork")
library("texreg")
library("viridisLite")
library("patchwork")
library("here")
#library("rethinking")
#library("statsExpressions")
#library("ggstatsplot")
library("ggthemes")
=library("rstan")
library("brms")
library("tidybayes")
library("bayesplot")
library("dagitty")
library("ggdag")
library("geepack")  # marginal structural models
library("ipw") # inverse probability weighting. 
library("WeightIt")# inverse probability weighting. 
library("mice")
rstan_options(auto_write=TRUE)
options(mc.cores=parallel::detectCores ())
theme_set(theme_few())
knitr::write_bib(c(.packages("geepack")))

cite_packages()
```

@@

df <- d %>%
  dplyr::mutate(male2 = ifelse(gender != "man", 1 , 2)) %>% # for index categorical variable, not change of meaning for gender. male and people who do not identify as male.
  dplyr::mutate(male = factor(ifelse(gender != "man", "male" , "notmale"))) %>%
  rename(
    rel_CHURCHFREQ   = rel_1,
    # factor need to recode (eg 7 as 0)// yikes factor transformed into a number
    rel_PRAYERFREQ = rel_2,
    # factor need to recode (eg. 7 as 0)// yikes factor transformed into a number
    IS_RELIIGOUS = rel_3,
    # factor 1 = yes, 2 = no, 3 = atheist// yikes factor transformed into a number
    BELONGS_DENOMINATION = rel_4,
    # relig
    rel_EXTENTBELIEVEGOD = rel_5,
    # do you belong to a religion or religious denomination? 1 = yes, 2 = no (!)
    rel_EXTENTBELIEVEAFTERLIFE = rel_6,
    rel_EXTENTSPIRITUAL  = rel_7,
    rel_IMPORTANCERELIGIOUSLIFE = rel_8,
    # 1 to five
    rel_IMPORTANCEBELIEVEGOD = rel_9,
    # 1 to five
    wb_genLIFEQUALITY = wb_gen_1,
    # not defined # also remove second underscore, which BRMS doesn't like
    wb_genSATHEALTH = wb_gen_2,
    # not defined
    wb_phyPAIN = wb_phys_1,
    wb_physNEEDSMEDICALTREAT =  wb_phys_2,
    wb_physHASENERGY =  wb_phys_3,
    wb_physMOBILITY = wb_phys_4,
    wb_physSLEEP = wb_phys_5,
    wb_physCANDODAILYACTIVITIES  = wb_phys_6,
    wb_physSATCAPACITYWORK  = wb_phys_7,
    wb_psychENJOYLIFE = wb_psych_1,
    wb_psychMEANING  = wb_psych_2,
    wb_psychCONCENTRATE  = wb_psych_3,
    wb_psychLIKESAPPEARANCE  = wb_psych_4,
    wb_psychSATSELF  = wb_psych_5,
    wb_psychANXIETY  = wb_psych_6,
    wb_socSATPERSONALRELATIONSHIPS  = wb_soc_1,
    wb_socSATSUPPORTFRIENDS  = wb_soc_2
    #   wb_socSATSEX   = wb_soc_3,
  ) %>%
  dplyr::mutate(
    IS_RELIIGOUS = as.factor(IS_RELIIGOUS),
    denomination = as.factor(denomination),
    ethnicity = as.factor(ethnicity),
    country = as.factor(country)
  ) %>%
  dplyr::mutate(
    IS_RELIIGOUS = recode_factor(
      IS_RELIIGOUS,
      "0" = "atheist",
      "0.5" = "not_religious",
      "1" = "religious"
    )
  )
max(df$rel_EXTENTBELIEVEGOD)
max(df$rel_CHURCHFREQ)

@@

```{r cache = TRUE}
library("naniar")
library(magick)
vis_miss(df) # substantial pattern of missingness in a few variables, 
df
df$wb_soc_3
dff<-df%>%
  select(-wb_soc_3)
sum(is.na(df$education))

miss_graph<- gg_miss_upset(dff)
miss_graph
miss_graph <-image_ggplot(miss_graph)
# save graph
str(miss_graph)

ggsave(miss_graph,
  path = here::here("figs"),
  width = 10,
  height = 5,
  units = "in",
  filename = "miss_graph.jpg",
  device = 'jpeg',
  limitsize = FALSE,
  dpi = 1200
)

@@

```{r}
library(mice)
library(tidyverse)
#d2<-mice(d1)
#d3<-complete(d2)
#saveRDS(d3,here::here("mods","d3"))
d3 <-readRDS(here::here("mods","d3"))
d4<-d3%>%
  select(anx, ch, bg, age, edu,male,ses,country)%>%
  drop_na()%>%
  mutate(anx_s = scale(anx),
         bg_s = scale(bg),
         ch_s = scale(ch),
         age_s = scale(age),
         edu_s = scale(edu),
         ses_s = scale(ses),
         male_2 =scale(as.numeric(male))/2,
         ses_s = scale(ses),
         country=as.factor(country))

@@

d4
dbl <- ipw::ipwpoint(
  exposure = bg_s,
  family = "gaussian",
  numerator = ~ 1,
  denominator = ~ age_s +ch_s + edu_s + male_2 + ses_s + country,
  trunc = 0.01,
  data = as.data.frame(d4)
)

@@

ipb_bg<- geeglm(
  anx_s ~ bg_s,
  data = d1p,  
  id = country,
  corstr = "exchangeable",
  weights = ipwBG
)
#saveRDS(ipb_bg, here::here("mods","ipb_bg"))

ipb_ch<- geeglm(
  anx_s ~  ch_s,
  data = d1p,  
  id = country,
  corstr = "exchangeable",
  weights = ipwCH
)
saveRDS(ipb_ch, here::here("mods","ipb_ch"))

@@

ipb_bg_noweights <- geeglm(
  anx_s ~ bg_s + ch_s + age_s + edu_s + male_2 + ses_s,
  data = d1p,  
  id = country,
  corstr = "exchangeable"
)
saveRDS(ipb_bg_noweights, here::here("mods","ipb_bg_noweights"))

ipb_ch_noweights <- geeglm(
  anx_s ~ ch_s + age_s + edu_s + male_2 + ses_s,
  data = d1p,  
  id = country,
  corstr = "exchangeable"
)
saveRDS(ipb_ch_noweights, here::here("mods","ipb_ch_noweights"))

msm_lmer <- lmer(
  anx_s ~ ch_s + age_s + edu_s + male_2 + ses_s +  (1+ ch_s|country),
  data = d1p, 
)
saveRDS(msm_lmer, here::here("mods","msm_lmer"))

msm_lmer_wg <- lmer(
  anx_s ~ ch_s + (1 + ch_s|country),
  weights = ipwCH,
  data = d1p
)
saveRDS(msm_lmer_wg, here::here("mods","msm_lmer_wg"))

model_parameters(ipb_bg_noweights)
model_parameters(ipb_bg_noweights)
model_parameters(ipb_bg)
model_parameters(ipb_bg)

model_parameters(ipb_ch_noweights)
model_parameters(ipb_ch)
model_parameters(ipb_ch)
model_parameters(msm_lmer)
model_parameters(msm_lmer_wg)

pred <- ggeffects::ggemmeans(msm_lmer_wg, terms = c("ch_s[all]"))
pred

plot(pred,
    # add.data=T,dot.alpha=.1, 
     facets = F)  + 
  scale_y_continuous(limits=c(-.7,.7)) + 
  theme_classic() + ggtitle("") # title to be suppled

@@

listout <- readRDS(here::here("mods","listout"))
modmc <- brm_multiple(
  anx_s ~ ch_s + age_s + edu_s + male_2 +ses_s + (1 + ch_s | country),
  data = listout,
  seed = 1234,
  warmup = 1000,
  iter = 2000,
  chains = 4,
  backend = "cmdstanr",
  file=  here::here("mods", "modmc.rds"),
  threads = threading(4)
)

#saveRDS(modmc, here::here("mods", "modmc.rds"))
summary(modmc)

```
## Bayesian wieghted regression

```{r}
listout <- readRDS(here::here("mods","listout"))
modmc_wt <- brm(
  anx_s|weights(ipwCH) ~ ch_s + (1 + ch_s | country),
  data = d1p,
  seed = 1234,
  warmup = 1000,
  iter = 2000,
  chains = 4,
  backend = "cmdstanr",
  file = here::here("mods","modmc_wt")
)
#saveRDS(modmc, here::here("mods", "modmc.rds"))
summary(modmc_wt)

```{r, cache = TRUE}
library(viridis)
p0<-brms::conditional_effects(modmc_wt, "ch_s", 
                              spaghetti = T,
                              ndraws = 1000,
                              categorical = F,
                              prob = .95,
                              method = 'fitted')

church_plot <- plot(p0, plot = FALSE)[[1]]   +  xlab("Service attendance (standardised)") + ylab ("Anxiety (standardised)") + labs(title = "Baysian Multi-level Model",
subtitle = "Inverse Probability Weighting") + scale_y_continuous(limits = c(-.5,.5))+ 
  theme_classic()
church_plot

ipw_gee <- plot(pred,
    # add.data=T,dot.alpha=.1, 
     facets = F)  + 
  scale_y_continuous(limits=c(-.1,.1)) + xlab("Service attendance (standardised)") + ylab ("Anxiety (standardised)") + 
  theme_classic() +labs(title = "Generalized Estimating Equations", 
  subtitle = "Inverse Probability Weighting") + scale_y_continuous(limits = c(-.5,.5))
ipw_gee
model_plot <- ipw_gee + church_plot
model_plot + plot_annotation(tag_levels = "a")

ggsave(
  model_plot,
  path = here::here("figs"),
  width = 10,
  height = 5,
  units = "in",
  filename = "model_plot.jpg",
  device = 'jpeg',
  limitsize = FALSE,
  dpi = 1200
)

@@

```{r}
library(ggplot2)
library(magick)
library(patchwork)

dag1 <- image_ggplot(image_read(here::here("figs","dg_1.tiff")),
                     interpolate = T)
dag1
dag2 <- image_ggplot(image_read(here::here("figs","dg_2.tiff")), interpolate = T)
dag2
dag3 <- image_ggplot(image_read(here::here("figs","dg_3.tiff")), interpolate = T)
dag3
dag4 <- image_ggplot(image_read(here::here("figs","dg_4.tiff")),
                     interpolate = T)
dag4
library(patchwork)
daggraph <- dag1 + dag4 + dag3  / ( dag2) + 
  plot_annotation(title = "Directed Acyclic Graphs (DAGs) clarify assumptions and hazards for causal identification", tag_levels = "a")

ggsave(
  daggraph,
  path = here::here("figs"),
  width = 10,
  height = 5,
  units = "in",
  filename = "daggraph.jpg",
  device = 'jpeg',
  limitsize = FALSE,
  dpi = 1200
)
```
